---
title: "Chapter 9. Support Vector Machine"
subtitle: "9.3 The Solution of Support Vector Machines & 9.4 Extension of Support Vector Machines Using a Kernel"
author: "Gayoung Moon"
date: "2025-05-29"
institute: Descendants of Lagrange \newline School of Mathematics, Statistics and Data Science \newline Sungshin Women’s University
fonttheme: "serif"
fontsize: 8pt
output:
  beamer_presentation:
    latex_engine: xelatex 
    theme: "metropolis"
header-includes:
  - \input{header_includes.tex}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# KKT conditions

## KKT(Karush-Kuhn-Tucker) conditions

- KKT conditions are necessary or sufficient conditions that an optimal solution must satisfy in a constrained nonlinear optimization problem.
\vt

- The KKT conditions are defined for optimization problems with the following constraints:

$$
\begin{aligned}
\min_{x \in \mathbb{R}^n} \; &f_0(x) \\
\text{subject to} \; &f_i(x) \leq0, \; i= 1, \cdots, m \\
& h_j(x)= 0, \; j= 1, \cdots, p.
\end{aligned}
$$

- $f_0(x)$: objective function, \newline
$f_i(x) \leq 0$: inequality constraints, \newline
$h_j(x)= 0$: equality constraints.

- And we express with the Lagrange function as:
$$
L(x, \alpha_i, \lambda_j):= f_0(x) + \sum_{i=1}^m \alpha_i f_i(x) + \sum^p_{j=1} \lambda_j h_j(x).
$$
  

## The Four Conditions of the KKT Conditions

- There are four conditions that must be satisfied for the solution $x^*$ to be the optimal solution:
\vt
1) Stationarity condition
$$
\nabla f_0(x^*) + \sum_{i=1}^m \alpha_i \nabla f_i(x^*) + \sum^p_{j=1} \lambda_j \nabla h_j(x^*)= 0,
$$
\vt
2) Primal feasibility condition
$$
f_i(x^*) \leq 0, \; h_j(x^*)= 0,
$$
\vt
3) Dual feasibility condition
$$
\alpha_i \geq 0 \; \text{for all } \, i,
$$
\vt
4) Complementary slackness condition
$$
\alpha_i f_i(x^*)=0 \; \text{for all } \, i.
$$


# The Solution of Support Vector Machines

## The Optimal Problem and the KKT Conditions in Support Vector Machine

- In support vector machine, the following optimization problem is solved:
$$
\begin{aligned}
\min_{\beta, \beta_0, \epsilon} \ &\frac{1}{2} \Vert \beta \Vert^2 + C\sum^N_{i=1} \epsilon_i \\
\text{subject to } \ &y_i(\beta_0 + x_i \beta) \geq 1- \epsilon_i, \\ &\epsilon_i \geq 0 \quad \forall i.
\end{aligned}
$$
\vt

- And the following seven equations are KKT conditions:
$$
\begin{array}{c}
y_i (\beta_0^* + x_i \beta^*) - (1- \epsilon_i^*) \geq 0 \\
\epsilon_i^* \geq 0 \\[1em]
\alpha_i [ y_i(\beta_0^* + x_i \beta^*) - (1- \epsilon_i^*) ] = 0 \\
\mu_i \epsilon_i^* = 0 \\[1em] 
\beta^*= \sum^N_{i=1} \alpha_i y_i x_i \in \mathbb{R}^p \\
\sum^N_{i=1} \alpha_i y_i = 0\\
C- \alpha_i - \mu_i = 0.
\end{array}
$$


## The KKT Conditions in SVM: Primal Feasibility Condition

- The first two conditions can be derived from the KKT condition (2):
$$
f_1(\beta^*), \cdots, f_m(\beta^*) \leq 0.
$$
\vt

- In the optimal problem of SVM, the original constraints are as follows:
$$
\begin{array}{c}
y_i(\beta_0 + x_i \beta) \geq 1 - \epsilon_i \quad \forall i= 1, \cdots, N \\
\epsilon_i \geq 0 \quad \forall i = 1, \cdots, N.
\end{array}
$$
\vt

- Thus, when the above two conditions, which are existing constraints, are satisfied, the optimal solution can be found.


## The KKT Conditions in SVM: Complementary Slackness Condition

- The two conditions in the second paragraph are derived from the KKT condition (4):
$$
\alpha_1 f_1(\beta^*)= \cdots = \alpha_m f_m(\beta^*)= 0.
$$

- Based on the optimization problem of SVM, the Lagrangian function is set as follows
$$
L_P := \frac{1}{2} \Vert \beta \Vert^2 + C \sum^N_{i=1} \epsilon_i - \sum^N_{i=1} \alpha_i \{ y_i(\beta_0 + x_i \beta) - (1- \epsilon_i) \} - \sum^N_{i=1} \mu_i \epsilon_i,
$$
and $\alpha_i$ and $\mu_i$ are the Lagrange multipliers.


- The relationship between the original constraints and the Lagrange multipliers $\alpha_i, \ \mu_i$ is as follows

$$
\begin{array}{c}
\alpha_i [y_i (\beta_0 + x_i \beta) - (1- \epsilon_i)] = 0 \\
\mu_i \epsilon_i = 0,
\end{array}
$$

then it means that one of the Lagrange multipliers and the constraints must have the value 0.


## The KKT Conditions in SVM: Stationarity Condition

- The last three conditions can be derived from the KKT condition (1):
$$
\nabla f_0(\beta^*) + \sum^m_{i=1} \alpha_i \nabla f_i (\beta^*)= 0.
$$
\vt

- Differentiating $L_P$ w.r.t $\beta, \beta_0, \epsilon_i$:
$$
\begin{aligned}
&\frac{\partial L_P}{\partial \beta}= \beta - \sum^N_{i=1} \alpha_i y_i x_i = 0 \Longrightarrow \beta= \sum^N_{i=1} \alpha_i y_i x_i \\
&\frac{\partial L_P}{\partial \beta_0}= -\sum^N_{i=1} \alpha_i y_i =0 \\
&\frac{\partial L_P}{\partial \epsilon_i}= C- \alpha_i - \mu_i = 0.
\end{aligned}
$$

- Then we obtain:
$$
\begin{array}{c}
\beta= \sum^N_{i=1} \alpha_i y_i x_i \\
\sum^N_{i=1} \alpha_i y_i = 0 \\
C- \alpha_i - \mu_i = 0.
\end{array}
$$


## SVM Primal Form: Applying KKT Conditions for Simplification

- We can construct the dual problem of $L_P$ from the primal problem.

- If we reconstruct the equation of $L_P$ using the equations differentiated by $\beta_0$ and $\epsilon_i$, we can write it as follows:
$$
\begin{aligned}
L_P &:= \frac{1}{2} \Vert \beta \Vert^2 + C \sum^N_{i=1} \epsilon_i - \sum^N_{i=1} \alpha_i \{ y_i(\beta_0 + x_i \beta) - (1- \epsilon_i) \} - \sum^N_{i=1} \mu_i \epsilon_i \\
&= \frac{1}{2} \Vert \beta \Vert^2 + C \sum^N_{i=1} \epsilon_i - \sum^N_{i=1} \alpha_i \{ y_i(\beta_0 + x_i \beta) - (1- \epsilon_i) \} - \sum^N_{i=1} (C- \alpha_i)\epsilon_i \\
&= \frac{1}{2} \Vert \beta \Vert^2 + C \sum^N_{i=1} \epsilon_i - C\sum^N_{i=1} \epsilon_i - \sum^N_{i=1} \alpha_i \{ y_i(\beta_0 + x_i \beta) \} + \sum^N_{i=1}\alpha_i - \sum^N_{i=1} \alpha_i \epsilon_i+ \sum^N_{i=1} \alpha_i \epsilon_i \\
&= \frac{1}{2} \Vert \beta \Vert^2 - \sum^N_{i=1} \alpha_i \{ y_i(\beta_0 + x_i \beta) \} + \sum^N_{i=1}\alpha_i \\
&= \frac{1}{2} \Vert \beta \Vert^2 - \beta_0 \sum^N_{i=1} \alpha_i y_i - \sum^N_{i=1} \alpha_i y_i x_i \beta + \sum^N_{i=1}\alpha_i = \frac{1}{2} \Vert \beta \Vert^2 - \sum^N_{i=1} \alpha_i y_i x_i \beta + \sum^N_{i=1}\alpha_i, \\
&\therefore L_P := \sum^N_{i=1}\alpha_i + \frac{1}{2} \Vert \beta \Vert^2 - \sum^N_{i=1} x_i \beta \alpha_i y_i.
\end{aligned}
$$


## Formulating the Dual using the Lagrange Multipliers

- The equation of $L_P$, reconstructed by the equation differentiate by $\beta$, change again as follows:
$$
\begin{aligned}
L_P &:= \sum^N_{i=1}\alpha_i + \frac{1}{2} \Vert \beta \Vert^2 - \sum^N_{i=1} x_i \beta \alpha_i y_i \\
&= \sum^N_{i=1}\alpha_i + \frac{1}{2} \bigg( \sum^N_{i=1} \alpha_i y_i x_i^{\top} \bigg)^{\top} \bigg( \sum^N_{j=1} \alpha_j y_j x_j^{\top} \bigg) - \sum^N_{i=1} x_i \bigg( \sum^N_{i=1} \alpha_i y_i x_i^{\top} \bigg) \alpha_i y_i \\
&= \sum^N_{i=1}\alpha_i - \frac{1}{2} \bigg( \sum^N_{i=1} \alpha_i y_i x_i^{\top} \bigg)^{\top} \bigg( \sum^N_{j=1} \alpha_j y_j x_j^{\top} \bigg) \\
&= \sum^N_{i=1}\alpha_i - \frac{1}{2} \sum^N_{i=1} \sum^N_{j=1} \alpha_i \alpha_j y_i y_j x_i x_j^{\top}.
\end{aligned}
$$

- So, we construct the function with input as the Lagrange coefficients $\alpha_i  \geq 0, \; i= 1, \cdots, N$:
$$
L_D := \sum^N_{i=1}\alpha_i - \frac{1}{2} \sum^N_{i=1} \sum^N_{j=1} \alpha_i \alpha_j y_i y_j x_i x_j^{\top}.
$$

- In this case, $\alpha$ ranges over $\sum^N_{i=1} \alpha_i y_i$ and $0 \leq \alpha_i \leq C$.


## Understanding Constraints in the Dual Problem

- In the dual objective function $L_D$, $\mu_i$ disappears, but the constraint that $\alpha_i$ has a range of $0 \leq \alpha_i \leq C$ still exists through the condition $\mu_i = C- \alpha_i$.
\vt
\vt

- By solving the dual problem under this constraint, we can obtain the values of $\alpha_i$. \newline
Then, the primal variable $\beta$ can be computed using:  
$$
\beta = \sum_{i=1}^N \alpha_i y_i x_i
$$
\vt
\vt

- And depending on the range of $\alpha_i$, it can be classified into three cases, which is the key to SVM interpretation.


## Solution of the Dual Problem According to $\alpha_i$ Range

- We can distinguish where each sample point is located based on the following three cases of $\alpha_i$: 
$$
\begin{cases}
\alpha_i = 0 \qquad \Longrightarrow y_i(\beta_0 + x_i \beta) > 1 \\
0 < \alpha_i < C \Longrightarrow y_i(\beta_0 + x_i \beta)= 1 \\
\alpha_i = C \qquad \Longrightarrow y_i(\beta_0 + x_i \beta) < 1.
\end{cases}
$$


## Solution of the Dual Problem According to $\alpha_i$ Range (Contd.)

- When $\alpha_i =0$, applying $C- \alpha_i - \mu_i= 0, \ \mu_i \epsilon_i = 0$, and $y_i (\beta_0 + x_i \beta) - (1- \epsilon_i) \geq 0$ in this order, we have:
$$
\alpha_i = 0 \Longrightarrow \mu_i = C > 0 \Longrightarrow \epsilon = 0 \Longrightarrow y_i (\beta_0 + x_i \beta) \geq 1.
$$

- When $0< \alpha_i <C$, from $\mu_i \epsilon_i = 0, \ C- \alpha_i - \mu_i= 0$, we have $\epsilon_i = 0$. Moreover, applying $\alpha_i [y_i (\beta_0 + x_i \beta) - (1- \epsilon_i)] = 0$, we have:
$$
0< \alpha_i <C \Longrightarrow y_i (\beta_0 + x_i \beta) - (1- \epsilon_i) = 0 \Longrightarrow y_i (\beta_0 + x_i \beta)=1.
$$

- When $\alpha_i =C$, from $\epsilon_i \geq 0$, we have $\epsilon_i \geq0$. Moreover, applying $\alpha_i [y_i (\beta_0 + x_i \beta) - (1- \epsilon_i)] = 0$, we have:
$$
\alpha_i =C \Longrightarrow y_i (\beta_0 + x_i \beta) - (1- \epsilon_i) = 0 \Longrightarrow y_i (\beta_0 + x_i \beta) \leq 1.
$$


## The Proof of the Optimal Solution in SVM

- As we have seen above, we show that at least one $i$ satisfies $y_i (\beta_0 + x_i \beta) = 1$.
\vt

- If there exists an $i$ such that $0< \alpha_i < C$ and at least one $\epsilon_i= 0$, then from the above, the $i$ satisfies $y_i(\beta_0 + x_i \beta)= 1$. \newline
That is, an optimal solution exists, which means that at least one support vector exists. In this case, we can obtain $\beta_0$ as $\beta_0 = y_1 - x_i \beta$.


## The Proof of the Optimal Solution in SVM (Contd.)

- Suppose $\alpha_1 = \cdots = \alpha_N = 0$, then we have $\beta = 0$ from $\beta= \sum \alpha_i y_i x_i$. \newline
Moreover, we have $\mu_i = C$ and $\epsilon_i= 0$, which means $y_i(\beta_0 + x_i \beta) \geq 1$ from $\mu_i \epsilon_i = 0$ and $C- \alpha_i - \mu_i = 0$. \newline
$\rightarrow$ Therefore, $\beta_0 = \pm 1$ satisfy $y_i(\beta_0 + x_i \beta)= 1$ when $y_i = \pm 1$. It means, there are not just one optimal solution.
\vt
\vt

- Next, we suppose that $\alpha_i = C$ for at least one $i$ and $\epsilon_i > 0$ for all $i$. \newline
If we define $\epsilon_* := \min_i \epsilon_i$, and replace $\epsilon_i \rightarrow \epsilon - \epsilon_*$, $\beta_0 \rightarrow \beta_0^{\prime} + y_i \epsilon_*$, respectively, the latter still satisfies the constraint:
$$
\begin{array}{c}
y_i \{ (\beta_0^{\prime} + y_i \epsilon_*) + x_i \beta \} - \{ 1 - (\epsilon - \epsilon_*) \} \geq 0, \\
\epsilon - \epsilon_* \geq 0.
\end{array}
$$
$\rightarrow$ Then, we can obtain a smaller value of $f_0(\beta, \beta_0, \epsilon) = \frac{1}{2} \Vert \beta \Vert^2 + C \sum_{i=1}^N \epsilon_i$, which contradicts the underlying assumption that $\beta, \beta_0, \epsilon$ was optimal.


## Solving the Dual Problem Using the Package in R

- We solve the dual problem of $L_D$ using a quadratic programming solver.
\vt

- In the R language, a package called **quadprog** is available for this purpose.
\vt

- To solve the dual problem in **R**, we transform $L_D = \sum^N_{i=1} \alpha_i - \frac{1}{2} \sum^N_{i, j= 1} \alpha_i \alpha_j y_i y_j x_i x_j^{\top}$ into the following matrix form:
$$
\begin{aligned}
&\text{minimize} \quad -\frac{1}{2} \alpha^{\top} D_{\text{mat}} \alpha + d_{\text{vec}}^{\top} \alpha, \\
&\text{subject to} \ \quad A_{\text{mat}} \alpha \geq b_{\text{vec}},\ \alpha \in \mathbb{R}^N.
\end{aligned}
$$

- $D_{\text{mat}} = (x_i y_i) (x_j y_j)^{\top} \in \mathbb{R}^{N \times N}$, \newline
$d_{\text{vec}} \in \mathbb{R}^N$: linear term of objective function, \newline
$A_{\text{mat}} \in \mathbb{R}^{m \times N}$: constraint matrix, \newline
$b_{\text{vec}} \in \mathbb{R}^m (m \geq 1)$: constrain right side.


## Solving the Dual Problem Using the Package in R (Contd.)

- In particular, in the formulation derived above, we take $m= 2N+1, \ meq = 1$,
$$
z= 
\begin{bmatrix}
x_{1, 1}y_1 & \cdots & x_{1, p} y_1 \\
\vdots & \vdots & \vdots \\
x_{N, 1} y_N & \cdots & x_{N, p}y_N
\end{bmatrix} \in \mathbb{R}^{N \times p}, \ A_{\text{mat}}= 
\begin{bmatrix}
y_1 & \cdots & y_N \\
-1 & \cdots & 0 \\
0 & \ddots & 0 \\
0 & \cdots & -1 \\
1 & \cdots & 0 \\
0 & \ddots & 0 \\
0 & \cdots & 1
\end{bmatrix} \in \mathbb{R}^{(2N+1) \times N},
$$
$D_{\text{mat}} = z z^{\top} \in \mathbb{R}^{N \times N}$, $b_{\text{vec}} = [ 0, -C, \cdots, -C, 0, \cdots, 0]^{\top} \in \mathbb{R}^{2N+1}, \ d_{\text{vec}}= [1, \cdots, 1]^{\top} \in \mathbb{R}^N$, and $\alpha= [\alpha_1, \cdots, \alpha_N] \in \mathbb{R}^N$.

```{r, echo= FALSE}
library(quadprog)
svm.1 = function(X,y,C){
eps=0.0001;n=nrow(X);meq=1
Dmat=matrix(nrow=n,ncol=n)
for(i in 1:n)for(j in 1:n) Dmat[i,j]=sum(X[i,]*X[j,])*y[i]*y[j]
Dmat=Dmat+eps*diag(n)
dvec= rep(1,n)
Amat=matrix(nrow=(2*n+1),ncol=n);Amat[1,]=y;Amat[2:(n+1),1:n]=-diag(n)
Amat[(n+2):(2*n+1),1:n]= diag(n); Amat=t(Amat)
bvec= c(0,rep(-C,n),rep(0,n))
alpha=solve.QP(Dmat,dvec,Amat,bvec=bvec,meq=1)$solution
beta=drop((alpha*y)%*%X)
index=(1:n)[eps<alpha&alpha<C-eps]
beta.0=mean(y[index]-X[index,]%*%beta)
return(list(beta=beta,beta.0=beta.0))
}
```


## [Example 1] Drawing the border of the SVM

- We generate samples and draw the border of the support vector machine.
```{r}
set.seed(924)
library(quadprog)
a=rnorm(1); b=rnorm(1); n=100;
X=matrix(rnorm(n*2),ncol=2,nrow=n); y=sign(a*X[,1]+b*X[,2]+0.1*rnorm(n))
plot(-3:3,-3:3,xlab="First Factor",ylab="Second Factor",
type="n")
for(i in 1:n){if(y[i]==1)points(X[i,1],X[i,2],col="red") else points(X[i,1],X[i
,2],col="blue")}
qq=svm.1(X,y,10); abline(-qq$beta.0/qq$beta[2],-qq$beta[1]/qq$beta[2])
```


# Extension of Support Vector Machines Using a Kernel

## Using the Kernel Function in SVM

- The reason for solving the dual rather than the primal is that the dual objective $L_D$ can be expressed using inner products $\langle \cdot, \cdot \rangle$ as
$$
L_D := \sum^N_{i=1} \alpha_i - \frac{1}{2} \sum^N_{i=1} \sum^N_{j=1} \alpha_i \alpha_j y_i y_j \langle x_i, x_j \rangle.
$$

- Let $V$ be the vector space with $\phi: \mathbb{R}^p \rightarrow V$, then we may replace $\langle x_i, x_j \rangle$ by $k(x_i, x_j) := \langle \phi(x_i), \phi(x_j) \rangle$.
\vt

- In such a case, we construct a nonlinear classification rule from $(\phi (x_1), y_1), \cdots, (\phi(x_N), y_N)$. \newline
$\rightarrow$ In other words, even if the mapping $\phi(x) \rightarrow y$ is linear and the learning is performed via a linear model, the original mapping $x \rightarrow y$ can still be nonlinear.


## Using the Kernel Function in SVM (Contd.)

- In the following, we construct a matrix $K$ such that the $(i, j)$-th element is $K_{i, j}= \langle\phi(x_i), \phi(x_j) \rangle \in V$.
\vt
\vt

- In fact, for $z \in \mathbb{R}^N$, the matrix
$$
\begin{aligned}
z^{\top} K z &= \sum^N_{i=1} \sum^N_{j=1} z_i \langle \phi(x_i), \phi(x_j) \rangle z_j \\
&= \langle \sum^N_{i=1} z_i \phi(x_i), \sum^N_{j=1} z_j \phi (x_j) \rangle \\
&= \Vert \sum^N_{i=1} z_i \phi(x_i) \Vert^2 \geq 0
\end{aligned}
$$
is symmetric and non-negative definite, and $k(\cdot, \cdot)$ is a kernel in the strict sense.


## Definition New Function **svm.2** using **svm.1**

- We modify the function **svm.1** as follows to define new function **svm.2**: \newline
1. add argument **K** to the function definition, \newline
2. replace sum(X[, i]*X[, j]) with **K(X[i, ], X[j, ])**, \newline
3. replace **beta** in **return()** with **alpha**.

```{r, echo= FALSE}
svm.2=function(X,y,C, K){
eps=0.0001; n=nrow(X); Dmat=matrix(nrow=n,ncol=n)

for(i in 1:n)for(j in 1:n) Dmat[i,j]=K(X[i,],X[j,])*y[i]*y[j]
Dmat=Dmat+eps*diag(n); dvec=rep(1,n)
Amat=matrix(nrow=(2*n+1),ncol=n); Amat[1,]=y; Amat[2:(n+1),1:n]=-diag(n);
Amat[(n+2):(2*n+1),1:n]=diag(n) ; Amat=t(Amat)
bvec=c(0,rep(-C,n),rep(0,n)); meq=1
alpha=solve.QP(Dmat,dvec,Amat,bvec=bvec,meq=1)$solution
index=(1:n)[eps<alpha&alpha<C-eps]
beta=drop((alpha*y)%*%X); beta.0=mean(y[index]-X[index,]%*%beta)
return(list(alpha=alpha,beta.0=beta.0))
}
```


## [Example 2] Comparison of Linear and Nonlinear Borders

- We generate samples and draw linear and nonlinear borders that are flat and curved surfaces.

```{r}
K.linear <-function(x,y) {return(t(x)%*%y)}
K.poly <-function(x,y) {return((1+t(x)%*%y)^2)}

library(quadprog)
# Function Definition
plot.kernel=function(K, lty){
qq=svm.2(X,y,1,K); alpha=qq$alpha; beta.0=qq$beta.0
f=function(u,v){x=c(u,v); S=beta.0; for(i in 1:n)S=S+alpha[i]*y[i]*K(X[i,], x);
return(S)}

u=seq(-2,2,.1);v=seq(-2,2,.1);w=array(dim=c(41,41))
for(i in 1:41)for(j in 1:41)w[i,j]=f(u[i],v[j])
contour(u,v,w,level=0,add=TRUE,lty=lty)
}

a=3; b=-1
n=200; X=matrix(rnorm(n*2),ncol=2,nrow=n); y=sign(a*X[,1]+b*X[,2]^2+0.3*
rnorm(n))
plot(-3:3,-3:3,xlab="X[,1]",ylab="X[,2]", type="n")
for(i in 1:n){
if(y[i]==1)points(X[i,1],X[i,2],col="red")
else points(X[i,1],X[i,2],col="blue")
}
plot.kernel(K.linear,1); plot.kernel(K.poly,2)
```


## [Example 3] Using the **e1071** Package in R

- Using the **e1071** package with the radial kernel, we draw a nonlinear surface.
\vt
  - Radial kernel: $K(x_i, x_j)= \exp(-\gamma \Vert x_i - x_j \Vert^2)$
  
- We can use **svm** function to specify parameter values such as $\gamma$ and kernel to be used for analysis.

```{r, warning=FALSE, out.width= '87%', fig.align='center'}
library(e1071)
x=matrix(rnorm(200*2), ncol=2); x[1:100,]=x[1:100,]+2; x[101:150,]=x[101:150,]-2
y=c(rep(1,150), rep(2,50)); dat=data.frame(x=x,y=as.factor(y))
train=sample(200,100)
svmfit=svm(y~., data=dat[train,], kernel ="radial", gamma=1, cost=100)
plot(svmfit, dat[train,])
```


## Q & A

\begin{center}
  {\bf {\Huge Q \& A}}
\end{center}


## 

\begin{center}
  {\bf {\Huge Thank you :)}}
\end{center}