---
title: "Chpater 5 : Infomation Criteria"
subtitle: "5.1.Information Criteria & 5.2.Efficient Estimation and the Fisher Information Matrix"
author: "Gayoung Moon"
date: "2025-03-16"
institute: Descendants of Lagrange \newline School of Mathematics, Statistics and Data Science \newline Sungshin Women’s University
fonttheme: "serif"
fontsize: 8pt
output:
  beamer_presentation:
    latex_engine: xelatex 
    theme: "metropolis"
header-includes:
  - \input{header_includes.tex}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
set.seed(1)
```

# Information Criteria


## Information Criterion

- **Information criterion** is an index for evaluating the validity of a statistical model from observation data.
\vt
\vt

- Information criterion refers to the evaluation of:
\vt
  - Fitness: how much the statistical model explains the data.
\vt

  - Simplicity: how simple the statistical model is.



## One of the Important Problems in Linear Regression

- One of the important problems in **linear regression**: \newline To select some $p$ covariates based on $N$ observations $(x_1, y_1), \cdots, (x_N, y_N) \in \mathbb{R}^p \times \mathbb{R}$.
\vt
\vt

- If there are too many covariates, then they overfit the data and try to explain the noise fluctuation by other covariates.



## Subset $S$ used as RSS$(S)$

- It isn't easy to choose $S \subseteq \{1, \cdots, p\}$ from the $2^p$ subsets when $p$ is large.
\vt

  - $2^p$ subsets: $\{\}, \{ 1\}, \cdots, \{ p\}, \{1, 2 \}, \cdots, \{1, \cdots, p \}$.
\vt
\vt

- We express the fitness and simplicity by the residual sum of square(RSS) value RSS$(S)$.
\vt

  - **RSS$(S)$** is based on the subset $S$ and the cardinality $k(S) := \vert S \vert$ of $S$.



## Property of the Subset $S$

$$
S \subseteq S' \Longrightarrow
\begin{cases}
\text{RSS}(S) \geq \text{RSS}(S') \\
k(S) \leq k(S')
\end{cases}.
$$

- It means that the larger the $k=k(S)$, the smaller $\hat{\sigma}_k^2 = \frac{\text{RSS}_k}{N}$ is, where $\text{RSS}_k := \min_{k(S)=k} \text{RSS}(S)$.



# AIC and BIC


## Defination of the AIC and BIC

- Akaike's Information Criterion(AIC) and the Bayesian Information Criterion(BIC) are well known.
\vt
\vt

- The AIC and BIC are defined by:
\vt

  - AIC $:= N \log{\hat{\sigma}_k^2} + 2k$.
\vt

  - BIC $:= N \log{\hat{\sigma}_k^2} + k \log{N}$.
\vt
\vt

- The coefficient of determination is:
\vt

  - $1 - \frac{\text{RSS}_k}{\text{TSS}}$.
\vt

  - It increases monotonically with $k$ and reaches its maximum value at $k= p$.



## Properties of the AIC and BIC

- The AIC and BIC values:
\vt

  - They decrease before reaching the minimum at some $0 \leq k \leq p$.
\vt

  - In the case of $k>p$, they increase.
\vt
\vt

- The adjusted coefficient of determination maximizes $1- \frac{\text{RSS}_k/(N-k-1)}{\text{TSS}/(N-1)}$ at some $0 \leq k \leq p$.
\vt

  - It is often much larger than those of the AIC and BIC.



# Example 45, 46


## [Example 45] Finding the Set of Covariates that minimizes the AIC and BIC

- In 'RSS.min(X, y, T)' function:
\vt
  - Input values: \newline
  X: Independent variables matrix $(n \times p)$, \newline
  y: Dependent variable vector $(n \times 1)$, \newline
  T: A combination(matrix) of X to select from.
  \vt

  - Output values: \newline
  value: Minimum of the RSS, \newline
  set: Combination of X with minimum RSS.
  \vt
  \vt
  
- 'RSS.min(X, y, T)' function is using the following formula:

$$
RSS = \sum^N_{i=1}(y_i - \hat{y_i})^2.
$$



## [Example 45] Finding the Set of Covariates that minimizes the AIC and BIC (Contd.)

- In 'AIC(BIC).min' function:
\vt
  
  - 'combn(1:p, k)' generates all combinations of $k$ variables out of a total of $p$.
  \vt
  
  - Output values: \newline
  AIC(BIC).min: Minimum of the AIC/BIC, \newline
  set.min: The combination of variables with the lowest AIC/BIC.
  \vt
  \vt

- 'AIC(BIC).min' function is using the following formula:

$$
\begin{aligned}
\text{AIC} &:= N \log{\hat{\sigma}_k^2} + 2k, \\
\text{BIC} &:= N \log{\hat{\sigma}_k^2} + k \log{N}.
\end{aligned}
$$



## [Example 45] Finding the Set of Covariates that minimizes the AIC and BIC (Contd.)

- In the AIC case:

```{r ex45-1, echo= TRUE, eval= FALSE}
RSS.min=function(X,y,T){
  m=ncol(T); S.min=Inf
  for(j in 1:m){
    q=T[,j]; S=sum((lm(y~X[,q])$fitted.values - y)^2)/n
  if(S<S.min){S.min=S; set.q=q}
  }
return(list(value=S.min,set=set.q))}
library(MASS)   # We use the Boston data set in the R MASS package.
df=Boston; X=as.matrix(df[,c(1,3,5,6,7,8,10,11,12,13)]); y=df[[14]];
# We assume the 'MEDV' variable is responses
# and the remaining variables are covariates.
p=ncol(X); n=length(y)
AIC.min=Inf
for(k in 1:p){
  T=combn(1:p,k); res=RSS.min(X,y,T)
  AIC= n*log(res$value/n)+2*k ##
  if(AIC<AIC.min){AIC.min=AIC; set.min= res$set}}
```



## [Example 45] Finding the Set of Covariates that minimizes the AIC and BIC (Contd.)

- AIC:

```{r ex45-2, echo= FALSE, eval= TRUE}
RSS.min=function(X,y,T){
  m=ncol(T); S.min=Inf
  for(j in 1:m){
    q=T[,j]; S=sum((lm(y~X[,q])$fitted.values - y)^2)/n
  if(S<S.min){S.min=S; set.q=q}
  }
return(list(value=S.min,set=set.q))
}

library(MASS)
df=Boston; X=as.matrix(df[,c(1,3,5,6,7,8,10,11,12,13)]); y=df[[14]];
p=ncol(X); n=length(y)
AIC.min=Inf
for(k in 1:p){
  T=combn(1:p,k); res=RSS.min(X,y,T)
  AIC= n*log(res$value/n)+2*k
  if(AIC<AIC.min){AIC.min=AIC; set.min= res$set}
}

AIC.min
set.min
```
\vt

- In the BIC case:
\vt
  - If we change the line '$\text{n}*\text{log(S.min)} + 2*\text{k}$' marked by **##** in the AIC code with '$\text{n}*\text{log(S.min)} + \text{k}*\text{log(N)}$', then the quantity becomes the BIC.
\vt

- BIC:
```{r ex45-4, echo= FALSE, eval= TRUE}
RSS.min=function(X,y,T){
  m=ncol(T); S.min=Inf
  for(j in 1:m){
    q=T[,j]; S=sum((lm(y~X[,q])$fitted.values - y)^2)/n
  if(S<S.min){S.min=S; set.q=q}
  }
return(list(value=S.min,set=set.q))
}

library(MASS)
df=Boston; X=as.matrix(df[,c(1,3,5,6,7,8,10,11,12,13)]); y=df[[14]];
p=ncol(X); n=length(y)
BIC.min=Inf
for(k in 1:p){
  T=combn(1:p,k); res=RSS.min(X,y,T)
  BIC= n*log(res$value/n)+k*log(n)
  if(BIC<BIC.min){BIC.min=BIC; set.min= res$set}
}

BIC.min
set.min
```
\vt

- Both AIC and BIC values have negative values. \newline
$\rightarrow$ It means that AIC and BIC may not be suitable as criteria for model selection because they are not close to 0.



## [Example 46] The Plot of Changes of AIC/BIC with # of Covariates

```{r ex46 plot, echo= FALSE}
RSS.min=function(X,y,T){
  m=ncol(T); S.min=Inf
  for(j in 1:m){
    q=T[,j]; S=sum((lm(y~X[,q])$fitted.values - y)^2)/n
    if(S<S.min){S.min=S; set.q=q}
  }
  return(list(value=S.min,set=set.q))
}

library(MASS)
df=Boston; X=as.matrix(df[,c(1,3,5,6,7,8,10,11,12,13)]); y=df[[14]];
n=nrow(X); p=ncol(X)
IC=function(k){
  T=combn(1:p,k);
  res=RSS.min(X,y,T)
  AIC= n*log(res$value/n)+2*k;
  BIC= n*log(res$value/n)+k*log(n)
  return(list(AIC=AIC,BIC=BIC))
}
AIC.seq=NULL; BIC.seq=NULL;
for(k in 1:p){AIC.seq=c(AIC.seq, IC(k)$AIC); BIC.seq=c(BIC.seq, IC(k)$BIC)}

plot(1:p, ylim=c(min(AIC.seq),max(BIC.seq)), type="n",xlab="# of variables",
     ylab="AIC/BIC", main= "Changes of AIC/BIC with # of Covariates")
lines(AIC.seq,col="red"); lines(BIC.seq,col="blue")
legend("topright",legend=c("AIC","BIC"), col=c("red","blue"), lwd=1, cex=.8)
```

- The BIC is larger than the AIC, but the BIC chooses a simpler model with fewer variables than the AIC.



# Efficient Estimator and the Fisher Infromation Matrix


## Probability Density Function of the Observations

- Suppose that:
\vt

  - $x_1, \cdots, x_N \in \mathbb{R}^{p+1}$
\vt

  - $y_1, \cdots, y_N \in \mathbb{R}$
\vt

  - Random variables: $e_1, \cdots, e_n \, = \varepsilon \, \sim N(0, \sigma^2)$
\vt

  - Unknown constants: $\beta_0 \in \mathbb{R}, \, \beta \in \mathbb{R}^p \; \rightarrow \, \beta \in \mathbb{R}^{p+1}$
\vt

  - In other words,

$$
X = \begin{bmatrix} x_1 \\
\vdots \\
x_N \end{bmatrix} \in \mathbb{R}^{N \times (p+1)}, \,
y= \begin{bmatrix} y_1 \\
\vdots \\
y_N \end{bmatrix} \in \mathbb{R}^N, \,
\beta = \begin{bmatrix} \beta_0 \\
\beta_1 \\
\vdots \\
\beta_p \end{bmatrix} \in \mathbb{R}^{p+1}.
$$
\vt

- The observations have been generated by the realizations $y_i= x_i \beta + \beta_0 + \varepsilon, \, i= 1, \cdots, N$ with random variables and unknown constants.



## Probability Density Function of the Observations (Contd.)

- When $f(y|x, \beta)$ follows a multivariate Gaussian distribution, the probability density function(PDF) can be written as follows:
\vt

$$
f(y|x, \beta) := \frac{1}{\sqrt{(2\pi \sigma^2)^{N}}} \exp \Big\{ -\frac{1}{2\sigma^2} \lVert y - x \beta \rVert^2 \Big\}.
$$



## The Value of $\hat{\beta}^{LSE}$ and the Likelihood

- $y = X\beta + \varepsilon$

- In the **least squares method**, we estimated $\beta$ by:

$$
\hat{\beta}^{LSE}= (X^{\top}X)^{-1}X^{\top}y.
$$
\vt

- $\hat{\beta}^{LSE}$ coincides with the $\beta \in \mathbb{R}^{p+1}$ that maximizes the likelihood

$$
\begin{aligned}
L :&= \prod^N_{i=1}f(y_i|x_i, \beta) \\
&= \prod^N_{i=1} \Bigg( \frac{1}{\sqrt{(2 \pi \sigma^2)}} \exp \Big\{ -\frac{1}{2\sigma^2} (y_i - x_i \beta)^2 \Big\} \Bigg).
\end{aligned}
$$



## Caculating log-likelihood

- The log-likelihood is written by:

$$
\begin{aligned}
\ell :&= \log{L} \\
&= \log{\prod^N_{i=1} \Bigg( \frac{1}{\sqrt{(2 \pi \sigma^2)}} \exp \Big\{ -\frac{1}{2\sigma^2} (y_i - x_i \beta)^2 \Big\} \Bigg)} \\
&= \log (2\pi \sigma^2)^{-\frac{N}{2}} + \log \prod^N_{i=1} \exp \Big\{ -\frac{1}{2\sigma^2} (y_i - x_i \beta)^2 \Big\} \\
&= -\frac{N}{2} \log(2 \pi \sigma^2) - \prod^N_{i=1} \frac{1}{2 \sigma^2} (y_i - x_i \beta)^2 \\
&= -\frac{N}{2} \log(2 \pi \sigma^2) - \frac{1}{2 \sigma^2} \lVert y - X \beta \rVert^2.
\end{aligned}
$$
\vt

- If $\sigma^2 > 0$ is fixed, \newline
maximizing $l$ is equivalent to minimizing $\lVert y - X \beta \rVert^2$.



## Differentiate log-likelihood with $\sigma^2$
  
- If we partially differentiate $\ell$ w.r.t. $\sigma^2$:
  
$$
\begin{aligned}
\frac{\partial \ell}{\partial \sigma^2}
&= \frac{\partial}{\partial \sigma^2} \Big( -\frac{N}{2} \log{(2 \pi \sigma^2)} - \frac{1}{2 \sigma^2} \lVert y - X \beta \rVert^2 \Big) \\
&= \frac{\partial}{\partial \sigma^2} \Big( -\frac{N}{2} \log{(2 \pi \sigma^2)} \Big) - \frac{\partial}{\partial \sigma^2} \Big( \frac{1}{2 \sigma^2} \lVert y - X \beta \rVert^2 \Big) \\
&= -\frac{N}{2}  \frac{1}{2 \pi \sigma^2}  2 \pi - \lVert y - X \beta \rVert^2 \big(-\frac{1}{2} \big) \frac{1}{(\sigma^2)^2} \\
&= - \frac{N}{2\sigma^2} + \frac{\lVert y - X \beta \rVert^2}{2(\sigma^2)^2} = 0.
\end{aligned}
$$
  
  

## Differentiate log-likelihood with $\sigma^2$ (Contd.)
  
- Using $\hat{\beta}= (X^{\top}X)^{-1}X^{\top}y$, we find:

$$
\hat{\sigma}^2 := \frac{1}{N} \lVert y - X \hat{\beta} \rVert^2 = \frac{1}{N} \lVert y - \hat{y} \rVert^2 = \frac{RSS}{N}.
$$
\vt
\vt

- It is the maximum likelihood estimate of $\hat{\sigma}^2$.



## Efficient Estimator and the Fisher Information Matrix

- Efficient Estimator:
\vt
  - When there are multiple unbiased estimators, the estimator with the smallest variance is called an efficient estimator.
\vt
\vt
\vt

- Let $\nabla \ell$ be the vector consisting of $\frac{\partial \ell}{\partial \beta_j}$, $j= 0, 1, \cdots, p$, \newline
$\rightarrow$ The fisher information matrix: \newline The covariance matrix $J$ of $\nabla \ell$ divided by $N$.



## Differentiation of the Score Function

- For $f^N(y|x, \beta) := \prod^N_{i=1} f(y_i|x_i, \beta)$,

$$
\begin{aligned}
\nabla \ell &= \frac{\nabla f^N(y|x, \beta)}{f^N(y|x, \beta)} \\
&= \frac{\nabla \prod^N_{i=1} f(y_i|x_i, \beta)}{f^N(y|x, \beta)} \\
&= \frac{\nabla \prod^N_{i=1} \Bigg( \frac{1}{\sqrt{(2 \pi \sigma^2)}} \exp \Big\{ -\frac{1}{2\sigma^2} (y_i - x_i \beta)^2 \Big\} \Bigg)}{f^N(y|x, \beta)} \\
&= \frac{f^N(y|x, \beta) \cdot \nabla \bigg( -\frac{1}{2\sigma^2} \sum^N_{i=1} (y_i - x_i \beta)^2 \bigg)}{f^N(y|x, \beta)} \\
&= \frac{f^N(y|x, \beta) \cdot \bigg( -\frac{1}{\sigma^2} \sum^N_{i=1} (y_i - x_i \beta)x_i \bigg)}{f^N(y|x, \beta)} \\
&= -\frac{1}{\sigma^2} \sum^N_{i=1} (y_i - x_i \beta)x_i.
\end{aligned}
$$



## Integral of $\nabla f^N(y|x, \beta)$

- If we partially differentiate both sides of $\int f^N(y|x, \beta) dy= 1$ w.r.t. $\beta$, \newline
we have that $\int \nabla f^N(y|x, \beta)dy= 0$.
\vt

$$
\begin{aligned}
\int \nabla f^N(y|x, \beta) \, dy
&= \int \nabla \prod^N_{i=1} \Bigg( \frac{1}{\sqrt{(2 \pi \sigma^2)}} \exp \Big\{ -\frac{1}{2\sigma^2} (y_i - x_i \beta)^2 \Big\} \Bigg) \, dy \\
&= \int f^N(y|x, \beta) \, \cdot \nabla \Bigg( -\frac{1}{2\sigma^2} \sum^N_{i=1} (y_i - x_i \beta)^2 \Bigg) \, dy \\
&= \int f^N(y|x, \beta) \cdot \Bigg( -\frac{1}{\sigma^2} \sum^N_{i=1}(y_i - x_i \beta) x_i \Bigg) \, dy \\
&= -\frac{1}{\sigma^2}\sum^N_{i=1} x_i \int (y_i - x_i\beta) \, f^N(y|x, \beta) \, dy \\
&= -\frac{1}{\sigma^2}\sum^N_{i=1} x_i \, E [y_i - x_i \beta] \\
&= -\frac{1}{\sigma^2}\sum^N_{i=1} x_i \, (x_i\beta - x_i\beta) = 0.
\end{aligned}
$$


## Expectation of the Score Function

- We have that:
  
$$
\begin{aligned}
E \nabla \ell \, &= \int \nabla l \, \cdot f^N(y|x, \beta) \, dy \\
&= \int \frac{\nabla f^N(y|x, \beta)}{f^N(y|x, \beta)} f^N(y|x, \beta) \,dy \\
&= \int \bigg( -\frac{1}{\sigma^2} \sum^N_{i=1} (y_i - x_i \beta)x_i \bigg) \, f^N(y|x, \beta) \, dy \\
&= -\frac{1}{\sigma^2}\sum^N_{i=1} x_i \int (y_i - x_i\beta) \, f^N(y|x, \beta) \, dy \\
&= -\frac{1}{\sigma^2}\sum^N_{i=1} x_i \, E [y_i - x_i \beta] \; = -\frac{1}{\sigma^2}\sum^N_{i=1} x_i \, \big( E[y_i] - x_i\beta \big) \\
&= -\frac{1}{\sigma^2}\sum^N_{i=1} x_i \, (x_i\beta - x_i\beta) \; = \int \nabla f^N(y|x, \beta) \; dy \; =0.
\end{aligned}
$$



## Differentiation of $E[ \nabla \ell]$

- And

$$
\begin{aligned}
0 &= \nabla \otimes [E\nabla \ell] \\
&= \nabla \otimes \int(\nabla l) f^N(y|x, \beta)dy \\
&= \int(\nabla^2 l) f^N(y|x, \beta)dy + \int(\nabla l) \{\nabla f^N(y|x, \beta) \}dy \\
&= \int \nabla \Big\{-\frac{1}{\sigma^2} \sum^N_{i=1} (y_i - x_i \beta)x_i \Big\} f^N(y|x, \beta) \, dy + \int \Big\{ -\frac{1}{\sigma^2} \sum^N_{i=1} (y_i - x_i \beta)x_i \Big\} \, \{ \nabla f^N(y|x, \beta) \} dy \\
&= \int \frac{1}{\sigma^2} \sum^N_{i=1} x_ix_i^{\top} \, f^N(y|x, \beta) \, dy \, + \, \int \Big\{ -\frac{1}{\sigma^2} \sum^N_{i=1} (y_i - x_i \beta)x_i \Big\} \, \Big\{ -\frac{1}{\sigma^2} \sum^N_{i=1} (y_i - x_i \beta)x_i \Big\} \, dy \\
&= \frac{1}{\sigma^2} \sum^N_{i=1} x_i x_i^{\top} \, \int f^N(y|x, \beta) \, dy \, + \, \int \Big\{ -\frac{1}{\sigma^2} \sum^N_{i=1} (y_i - x_i \beta)x_i \Big\}^2 \, dy \\
&= \frac{1}{\sigma^2} \sum^N_{i=1} x_i x_i^{\top} \, + \, \int \Big\{ -\frac{1}{\sigma^2} \sum^N_{i=1} (y_i - x_i \beta)x_i \Big\}^2 \, dy \\
&= E[\nabla^2 \ell] + E[(\nabla \ell)^2].
\end{aligned}
$$



## The Covariance Matrix $J$ of $\nabla \ell$

- We can verify that it is as follows:

$$
E[\nabla^2 \ell] + E[(\nabla \ell)^2] = 0.
$$

$$
\therefore \, E[(\nabla \ell)^2] = -E[\nabla^2 \ell].
$$
\vt
\vt

- Then, the above equation implies that:

$$
J = \frac{1}{N}E[(\nabla \ell)^2] = -\frac{1}{N}E[\nabla^2 \ell].
$$



# $Cram \acute{e} r-Rao$ Inequality


## $Cram \acute{e} r-Rao$ Inequality

- $Cram \acute{e} r-Rao$ inequality is:
\vt
  - Inequality that gives a lower bound on the variance of the discomfort estimate.
\vt

  - It is expressed as the inverse matrix of the fisher information matrix.
  
$$
Var(\tilde{\beta}) \geq (NJ)^{-1}.
$$
\vt
\vt

- $\tilde{\beta} \in \mathbb{R}^{(p+1)}$: unbiased estimator.
\vt

- $(NJ)^{-1}$: the fisher information matrix $\in \mathbb{R}^{(p+1) \times (p+1)}$.



## Definition of log-likelihood Function and Score Function

- We defined the log-likelihood function above as follows:

$$
\ell := \log L = -\frac{N}{2} \log(2 \pi \sigma^2) - \frac{1}{2 \sigma^2} \rVert y - X \beta \lVert^2.
$$

- And we can also define the score function as the slope of the log-likelihood:

$$
\nabla \ell:= -\frac{1}{\sigma^2} \sum^N_{i=1} (y_i- x_i \beta)x_i.
$$



## Definition of the Fisher Information Matrix

- The fisher information matrix $J$ is expressed as the square of the expectation of the score function.

$$
J = \frac{1}{N} E[(\nabla \ell)^2] = \frac{1}{N \sigma^4} E[\sum^N_{i=1}(y_i - x_i \beta)^2 x_i]
$$

- In Gaussian distribution, $E[(y_i - x_i \beta)^2] = \sigma^2$:

$$
J = \frac{1}{N \sigma^2} \sum^N_{i=1} x_i.
$$



## Propositoin of $Cram \acute{e} r-Rao$ Inequality

- The least squares estimate satisfies the equality part of the inequality.
\vt
\vt

- We know $\int f^N(y| x, \beta)= 1$ and this end, if we partially differentiate both sides of 

$$
\int \tilde{\beta_i} f^N(y| x, \beta) dy = \beta_i
$$
w.r.t $\beta_j$, we have the following equation:

$$
\int \tilde{\beta_i} \frac{\partial}{\partial \beta_j} f^N(y| x, \beta)dy = 
\begin{cases}
 1, i=j \\
 0, i \neq j
\end{cases}.
$$



## Propositoin of $Cram \acute{e} r-Rao$ Inequality (Contd.)

- If we write this equation in terms of its covariance matrix, we have that $E[\tilde{\beta} (\nabla \ell)^{\top}]= I$, where $I$ is a unit matrix of size $(p+1)$.
\vt
\vt

- And we know $E[\nabla \ell]=0$, we rewrite the above equation as follows:

$$
E[(\tilde{\beta} -\beta)(\nabla \ell)^{\top}] = I.
$$



## Propositoin of $Cram \acute{e} r-Rao$ Inequality (Contd.)

- Then, the covariance matrix of the vector of size $2(p+1)$ is:

$$
\begin{bmatrix}
V(\tilde{\beta}) & I \\
I & NJ
\end{bmatrix}.
$$
\vt
\vt

- Because both $V(\tilde{\beta})$ and $J$ are covariance matrices, they are non-negative definite.
\vt
  - Non-negative definite: \newline
  Let $A$ be an $n \times n$ real symmetric matrix, $A$ is **non-negative definite** if:
  
$$
xAx \geq 0, \; \text{for any} \, x \in \mathbb{R}^n.
$$



## Propositoin of $Cram \acute{e} r-Rao$ Inequality (Contd.)

- Then, we claim that both sides of matrixes are non-negative definite:

$$
\begin{bmatrix}
V(\tilde{\beta})-(NJ)^{-1} & 0 \\
0 & NJ
\end{bmatrix} =
\begin{bmatrix}
I & -(NJ)^{-1} \\
0 & I
\end{bmatrix}
\begin{bmatrix}
V(\tilde{\beta}) & I \\
I & NJ
\end{bmatrix}
\begin{bmatrix}
I & 0 \\
-(NJ)^{-1} & I
\end{bmatrix}.
$$

- For an arbitrary $x \in \mathbb{R}^n$, if $xAx \geq 0$, for an arbitrary $B \in \mathbb{R}^{n \times m}$ and $y \in \mathbb{R}^m$, we have that $yBABy \geq 0$, which means that $V(\tilde{\beta}) - (NJ)^{-1}$ is non-negative definite.
\vt

- So, we have the conclusion:

$$
\therefore V(\tilde{\beta}) \geq (NJ)^{-1}.
$$



## Q & A

\begin{center}
  {\bf {\Huge Q \& A}}
\end{center}



## 

\begin{center}
  {\bf {\Huge Thank you :)}}
\end{center}